Untitled

### 2022-06-02 Supplementary_Material/Subset_spp_floral_rewards_and_completecases_PPCA.Rmd
Supp mat update

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,4.8,5.4,5,4.2,5.8,3.4)+c(0,0,0,0,0,0,0,0)), y = -(PCAloadings$PC2*c(4.693,3.5,4,4,3,4.15,4.2,6.2)),
                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)

>>>>

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,4.8,5.4,5,4.2,5.8,3.4)+c(0,0,0,0,0,0,0,0)), y = -(PCAloadings$PC2*c(4.693,3.5,4,4,3,4.15,4.2,6.5)),
                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)

### 2022-06-02 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Ecology_Letters.Rmd
Supp mat update

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig. S3.}  Phylogenetic informed principal component analysis for the species that did not have missing values."}
setwd("~/R_Projects/Reproductive Traits")

@@

pc3 <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

@@

  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
 #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
 # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
 # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
 # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
 # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
 # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
 # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
 # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
 # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
 # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
 # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)

      #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )

@@

pc3(PC)

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=24, fig.width=24,  fig.cap="\\textbf{Fig. S4.} Fitted posterior estimates of the interaction (yes/no) and number of visits made by bees including and exluding honey bees on the main axes of trait variation. The superior panel (plots a, b c, d, e and f) shows the comparison for presence-absence and the lower panel (plots g, h, i, j, k and l) the comparison for visitation rates."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Fig. S5.} Regression tree analyses. Comparison of the regression tree analyses between the full set of species and the subset of species with floral rewards for each plant species level metric. "}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10,  fig.cap="\\textbf{Fig. S6.} PC1 and PC3 of the phylogenetically informed principal component analysis with the full set of species."}
setwd("~/R_Projects/Reproductive Traits")

pc3 <- function(PC, x="PC1", y="PC3") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
  plot <- plot + ylab(paste("PC3 ", "(",(percentage[3]),"%",")", sep = "")) #YLAB

  plot <- plot + theme_bw() #+ annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
 #  annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
 # annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
 # annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
 # annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
 # annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
 # annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
 # annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
 # annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
 # annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
 # annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
 # annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)

      #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
 plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,4.8,7.1,5.5)), y = -(PCAloadings$PC2*c(-3.2,4.5,3.75,8.4,5,5.5)+c(0,0,0,0,-0.08,0)),
                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)

pc3(PC)

>>>>

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=20, fig.width=10,out.width="80%",fig.align='center',fig.cap= "\\textbf{Fig. S3.} Comparison of the phylogenetic informed principal component analysis for the dataset with data imputation and without data imputation. Panel A shows the reproductive spectrum of trait variation for the full dataset with data imputation and panel B shows the reproductive spectrum for the dataset without data imputation where the species with missing trait data were excluded from the analysis."}

#Load libraries
library(viridis) #COLOUR GGPLOT
library(ggplot2)
library(broman) #crayon colours
library(cowplot)
library(magick)

# Theme for publication
theme_ms <- function(base_size=12, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
      theme(text=element_text(color="black"),
            axis.title=element_text( size = rel(1.75)),
            axis.text=element_text(size = rel(1.75), color = "black"),
            legend.title=element_text(face="bold"),
            legend.text=element_text(),
            legend.background=element_rect(fill="transparent"),
            legend.key.size = unit(1.2, 'lines'),
            panel.border=element_rect(color="black",size=1),
            panel.grid.minor.x =element_blank(),
            panel.grid.minor.y= element_blank(),
             panel.grid.major= element_blank()
      ))
}

#Images were made by Paula Martin
#Check her work on https://paulamartinart.com/

#ADD LABELS
  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
 plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
                         label = PCAloadings$Variables, color="black",fontface =2,size=4)

# plot <- plot + annotate("text", x = #(PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = #(PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0))#,
#                         label =c("Low selfing", "Few flowers", #"Small flowers", "Short styles", "Few ovules", "Short plants" ), #color="black",fontface =2,size=4)

p1 <- all_spp(PC)

@@

all_complete_cases <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

@@

  plot <- plot + theme_bw() 
      #ADD LABELS
  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )

@@

p2 <- all_complete_cases(PC)

library(patchwork)

p1 / p2 + plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 24, face="bold"))

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=20, fig.width=10,out.width="80%",fig.align='center',fig.cap="\\textbf{Fig. S4.} Comparison of the phylogenetic informed principal component analysis for the subset of species that had information of floral rewards with data imputation and without data imputation. Panel A shows the reproductive spectrum of trait variation for the dataset with data imputation and panel B shows the reproductive spectrum for the dataset excluding species with missing trait data"}
setwd("~/R_Projects/Reproductive Traits")

  #ADD LABELS
  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants", "Copious nectar","Copious pollen")

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.85,4.8,4.8,5.5,5.5,5.5,5.8,6.5)), y = -(PCAloadings$PC2*c(4.8,4.4,4.15,5.35,4.2,4.7,5.75,6)+c(0,0,0,0,0,0,0,0)),
                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)

p1 <- all_spp(PC)

#Load data
phyl_pca_forest_nectar_pollen <- readRDS("Data/RData/phyl_pca_forest_nectar_pollen_complete_cases.rds")
dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA_nectar_pollen_complete_cases.rds")

#############################################################################################################################################################
#COMPATIBILITY
#############################################################################################################################################################
#Load plots
PC$S[,1] <- -PC$S[,1]
PC$S[,2] <- -PC$S[,2]

all_spp_complete <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  plot <- plot + geom_point(data=dat, aes(x, y),size=0.95, color="black")

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=-v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))

  #ADD LABELS
  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants", "Copious nectar","Copious pollen")

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,4.8,5.4,5,4.2,5.8,3.4)+c(0,0,0,0,0,0,0,0)), y = -(PCAloadings$PC2*c(4.693,3.5,4,4,3,4.15,4.2,6.5)),
                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)

p2 <- all_spp_complete(PC)

library(patchwork)

p1 / p2 + plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 24, face="bold"))

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=24, fig.width=24,  fig.cap="\\textbf{Fig. S5.} Fitted posterior estimates of the interaction (yes/no) and number of visits made by bees including and exluding honey bees on the main axes of trait variation. The superior panel (plots a, b c, d, e and f) shows the comparison for presence-absence and the lower panel (plots g, h, i, j, k and l) the comparison for visitation rates."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Fig. S6.} Regression tree analyses. Comparison of the regression tree analyses between the full set of species and the subset of species with floral rewards for each plant species level metric. "}

@@
